CRUSE to Safe Cycling in Ireland

### 2023-09-13 paper.qmd
Sentence breaks

---
title: "CRUSE to Safe Cycling in Ireland"
subtitle: An Open Source Methodology to Support Active Travel
bibliography: bibliography.bib
csl: apa.csl

@@

>>>>

---
title: "CRUSE to Safe Cycling in Ireland"
subtitle: An Open Source Methodology to Support Active Travel
bibliography: bibliography.bib
csl: apa.csl
editor:
  markdown:
    wrap: sentence

@@

Despite these advances, the PCT approach outlined in previous research paper had limitations:

-   Limited coverage of modes beyond travel to work and school

-   ...
